---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# maplayer

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/maplayer)](https://CRAN.R-project.org/package=maplayer)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
 [![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

The goal of maplayer is to provide a consistent set of functions for creating map layers using simple feature ({sf}) data, the {ggplot2} package, and a variety of ggplot2 extension packages.

The functions in maplayer started as part of the {overedge} package and re-exports several key functions from that package. It also includes layer functions that had been part of the birdseyeview package. The intention is to consoldiate all of the map layer functions into a single package as the first step in the process of splitting overedge into multiple packages.

## Installation

You can install the development version of maplayer like so:

``` r
remotes::install_github("elipousson/maplayer")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r setup}
library(maplayer)
library(ggplot2)
library(sf)
```

### Make icon maps with sf objects and ggplot2

`layer_icon` wraps [ggsvg::geom_point_svg()] to provide an convenient way to make icon maps.

You can create maps using a single named icon that matches one of the icons in [overedge::map_icons].

```{r}
nc <- st_read(system.file("shape/nc.shp", package = "sf"))
nc <- st_transform(nc, 3857)
theme_set(theme_void())

nc_map <-
  ggplot() +
  geom_sf(data = nc)

nc_map +
  layer_icon(data = nc, icon = "point-start", size = 8)
```
